Compositional Verification of Concurrent C Programs with Search Structure Templates

### 2023-05-02 concurrency/CONCUR 2023/paper.tex
unify infp and node_ref

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% spec of inRange
		{\color{blue}
			\forall \  m. \left\langle
			\begin{array}{c}
				\texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ \infp (\texttt{n}) \ \big| \ \treerep\ m
			\end{array}
			\right\rangle
		}
		\\ 
		\texttt{traverse(pn, k)} 
		\\
		{\color{blue}
			\left\langle \mathit{res}. \ \exists \ \texttt{n'}.
			\begin{array}{l}
				\texttt{pn} \mapsto (\texttt{n', n'}) \ \ast \ (\mathit{res} \leftrightarrow (\texttt{n'->t} = \texttt{NULL}))  \ \ast \ 
				\\ \infp(\texttt{n'}) \ \ast \ \mathsf{R}(\texttt{n'}) \ \ast \ \texttt{k} \in \mathsf{range}(\texttt{n'})
			\end{array}
			\ \Bigg| \ \treerep\ m \
			\right\rangle
		}
	\end{mathpar}
	\caption{Specification of \texttt{traverse} for the give-up template}
	\label{fig:traverse_giveup}
\end{figure}

The give-up template's \texttt{traverse} specification, shown in Figure \ref{fig:traverse_giveup},  is simpler than that of the lock-coupling template. The local precondition does not hold any locks, consisting only of $\infp(\texttt{n})$, a footprint predicate asserting that node \texttt{n} is included in the search structure's abstract state $m$. \wm{Should we unify $\infp$ and $\nodeboxrep$?} As before, the \texttt{traverse} function will navigate the structure and return a node \texttt{n'} whose range includes \texttt{k}, as well as acquiring \texttt{n'}'s lock and returning its contents $\mathsf{R}(\texttt{n'})$. Also as before, the Boolean $\mathit{res}$ indicates whether \texttt{n'->t} is \texttt{NULL} or not.

@@

\begin{figure}[!ht]
	$\color{blue}
	\forall \  m. \left\langle
	\begin{array}{c}
		\texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ \infp (\texttt{n}) \ \big| \ \treerep\ m
	\end{array}
	\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_traverse.c}
	$\color{blue}
	\left\langle \mathit{res}. \ \exists \ \texttt{n'}.
	\begin{array}{l}
		\texttt{pn} \mapsto (\texttt{n', n'}) \ \ast \ (\mathit{res} \leftrightarrow (\texttt{n'->t} = \texttt{NULL}))  \ \ast \ 
		\\ \infp(\texttt{n'}) \ \ast \ \mathsf{R}(\texttt{n'}) \ \ast \ \texttt{k} \in \mathsf{range}(\texttt{n'})
	\end{array}
	\ \Bigg| \ \treerep\ m \
	\right\rangle$
	\caption{The \texttt{traverse} function in give-up template annotated with separation logic specification}
	\label{proof_giveup_traverse}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\begin{mathpar}
		% spec of inRange
		{\color{blue}
			\forall \  m. \left\langle
			\begin{array}{c}
				\texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ \nodeboxrep(\texttt{n}) \ \big| \ \treerep\ m
			\end{array}
			\right\rangle
		}
		\\ 
		\texttt{traverse(pn, k)} 
		\\
		{\color{blue}
			\left\langle \mathit{res}. \ \exists \ \texttt{n'}.
			\begin{array}{l}
				\texttt{pn} \mapsto (\texttt{n', n'}) \ \ast \ (\mathit{res} \leftrightarrow (\texttt{n'->t} = \texttt{NULL}))  \ \ast \ 
				\\ \nodeboxrep(\texttt{n'}) \ \ast \ \mathsf{R}(\texttt{n'}) \ \ast \ \texttt{k} \in \mathsf{range}(\texttt{n'})
			\end{array}
			\ \Bigg| \ \treerep\ m \
			\right\rangle
		}
	\end{mathpar}
	\caption{Specification of \texttt{traverse} for the give-up template}
	\label{fig:traverse_giveup}
\end{figure}

The give-up template's \texttt{traverse} specification, shown in Figure \ref{fig:traverse_giveup},  is simpler than that of the lock-coupling template. The local precondition does not hold any locks, consisting only of $\infp(\texttt{n})$, a footprint predicate asserting that node \texttt{n} is included in the search structure's abstract state $m$. It is written formally as
$\nodeboxrep(\texttt{n}) \triangleq\ \infp(\texttt{n})$.
%\wm{Should we unify $\infp$ and $\nodeboxrep$?} 
As before, the \texttt{traverse} function will navigate the structure and return a node \texttt{n'} whose range includes \texttt{k}, as well as acquiring \texttt{n'}'s lock and returning its contents $\mathsf{R}(\texttt{n'})$. Also as before, the Boolean $\mathit{res}$ indicates whether \texttt{n'->t} is \texttt{NULL} or not.

@@

\begin{figure}[!ht]
	$\color{blue}
	\forall \  m. \left\langle
	\begin{array}{c}
		\texttt{pn} \mapsto (\texttt{p, n}) \ \ast \ \nodeboxrep(\texttt{n}) \ \big| \ \treerep\ m
	\end{array}
	\right\rangle$
		\lstinputlisting[language=C, style=myStyle, mathescape=true]{proof_giveup_traverse.c}
	$\color{blue}
	\left\langle \mathit{res}. \ \exists \ \texttt{n'}.
	\begin{array}{l}
		\texttt{pn} \mapsto (\texttt{n', n'}) \ \ast \ (\mathit{res} \leftrightarrow (\texttt{n'->t} = \texttt{NULL}))  \ \ast \ 
		\\ \nodeboxrep(\texttt{n'}) \ \ast \ \mathsf{R}(\texttt{n'}) \ \ast \ \texttt{k} \in \mathsf{range}(\texttt{n'})
	\end{array}
	\ \Bigg| \ \treerep\ m \
	\right\rangle$
	\caption{The \texttt{traverse} function in give-up template annotated with separation logic specification}
	\label{proof_giveup_traverse}
\end{figure}
